---
title: "Add custom labels to a new repo"
date: "Created: 2024-04-27 | Updated: `r format(Sys.Date(), '%Y-%m-%d')`"
output: 
  html_document:
    code_folding: "hide"
params:
  evaluate: TRUE
---

```{r setup}
knitr::opts_chunk$set(
  echo=TRUE, 
  include = TRUE,
  message=FALSE, 
  warning=FALSE, 
  dpi=60, 
  out.width = "100%", 
  # note the use of a param here! We only want to run the script once so we will turn this off after we do that.
  eval = params$evaluate)
options(scipen=999)
options(knitr.kable.NA = '--')
options(knitr.kable.NAN = '--')
```

Here is a bit of tutorial file name setup. We use these to define the input and output files for the script.
```{r name-outputs}
file_in <- 'scripts/tutorials/setup-github-issue-labels.Rmd'
# This assumes we use the same name and directory for the html output file as the Rmd input file
file_out <- paste0(
  basename(
    tools::file_path_sans_ext(file_in)
  ), 
  '.html'
)
```


First we make a list of the labels we want:

```{r name-issue-labels}
# make a list of our custom labels to add
issue_labels <- c(
  "high priority",
  "moderate priority",
  "low priority",
  "data management",
  "photos",
  "documentation"
)
```


<br>

Let's have a look at those:

`r cat(knitr::combine_words(issue_labels, before = "- ", after = "\n", sep = "\n", , and = ""))`

<br>


Sweet - now define our repo specific params. We could do this n hte `yaml` header of this document but
that would mean that we could not run the script chunk by chunk (or I don't know how anyway).
```{r name-repo-params}
repo_owner <- "NewGraphEnvironment"
repo_name <- "mybookdown-template"

```

<br>

Make an issue in our repo to add our custom labels and capture the output returned from the request as `o`.
```{r post1}
o <- gh::gh(
  endpoint = "POST /repos/{owner}/{repo}/issues",
  title = "Set up custom labels for this repo",
  body = "This is a remotely triggered issue to add custom labels to this repo.",
  owner = repo_owner,
  repo = repo_name
)

```

<br>


Add the list of labels to the repo. Reference the issue number grabbed from the captured output of the request
that made the issue.
```{r post2}
# add them to the repo
gh::gh(
  endpoint = "POST /repos/{owner}/{repo}/issues/{issue_number}/labels",
  owner = repo_owner,
  repo = repo_name,
  issue_number = o$number,
  labels = issue_labels
)

```

<br>

Now we can see the labels have been added to the repo so add a new comment on it then close the issue.

<br>

**DANGER DAN - We cannot do these things in one API request because the endpoints are different.** If we post a
`body` to the `POST /repos/{owner}/{repo}/issues/{issue_number}` endpoint while we are closing the `state`, 
it will edit the very first comment!! Not something we want to do!!  If we did want to
change the initial comment we should probably capture what it was, ~~strikethrough~~ it, and then add a new comment. That is a journey for another time.

<br>

Seperately we:

  1. add a comment



```{r post3}
gh::gh(
  endpoint = "POST /repos/{owner}/{repo}/issues/{issue_number}/comments",
  owner = repo_owner,
  repo = repo_name,
  body = "got er done!",
  issue_number = o$number
)
```

<br>

  2. close the issue.
```{r post4}
gh::gh(
  endpoint = "POST /repos/{owner}/{repo}/issues/{issue_number}",
  owner = repo_owner,
  repo = repo_name,
  state = "closed",
  issue_number = o$number
)
```

Banger. We are done.  In order to render this document to html, we need to run the following code IN THE CONSOLE.  There are `environment` things in play when inside of a bookdown project that I do not 
quite understand so that is how I am doing it for now.

```{r render, eval = FALSE}
rmarkdown::render(input = file_in, output_file = file_out)
```

